---
title: "Seeding in Social Networks"
author: "Sourish, Rohen and Rajan"
institute: "School of Mathematics and Statistics, University of Sydney"
date: "DATA5441 Project 10"
output:
  xaringan::moon_reader:
    css: [default, metropolis, chocolate-fonts, "styler.css", "pres_slides_files/rajan_usyd_custom.css"]
    lib_dir: pres_slides_files/themes
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, 
                      fig.align = "center", out.width = "100%")



library(tidyverse)
library(plotly)
```

<!-- <style> -->
<!--   .superbigimage{ -->
<!--       overflow-x:scroll; -->
<!--       white-space: nowrap; -->
<!--   } -->

<!--   .superbigimage img{ -->
<!--      max-width: none; -->
<!--   } -->
<!-- </style> -->


class: inverse, center, middle

# Background

---

# Background

- What are seeds?
- Seeding methods
- Leveraging the friendship paradox

---

class: inverse, center, middle

# Problem introduction

---

# Problem introduction

## Alexander et al.

- Pair has higher diffusion to non targeted nodes 
- Two seed triangles cause higher prob of adoption

---

# Problem introduction

## What we looked at

- How successful was each seeding method in reaching more central nodes (correlation between seeding vs. centrality)? <!-- might be able to explain result in alexander -->
- Does the seeding method impact the number of two-seed triangles?
- Does the seeding method impact the spread of innovations in a simple threshold model?

---

class: inverse, center, middle

# Problem introduction

---



# Plots

<!-- <div class="superbigimage"> -->
<!-- </div> -->


<!-- <iframe src = "plotly_figures/twoSeedTransMainFigure.html" width = "400" height = "400" frameborder="0"></iframe -->

```{r}
g = readRDS("plotly_figures/twoSeedTransMainFigure.RDS")
#   + theme(axis.title.y = element_text(size = rel(0.8)))
ggplotly(g)

```


---

```{r}
g = readRDS("plotly_figures/degreeVStriangles.RDS")
ggplotly(g)

```


---

```{r}
g = readRDS("plotly_figures/maxDegreeVSdifference.RDS")
ggplotly(g)
```

---


```{r}
g = readRDS("plotly_figures/nVScascade.RDS")
# g = g  +
#   theme(axis.title.y = element_text(size = rel(0.8), angle = 90))
ggplotly(g)

```

---
```{r}
g = readRDS("plotly_figures/qVSprop.RDS")
# g = g  +
#   theme(axis.title.y = element_text(size = rel(0.8), angle = 90))
ggplotly(g)
```






```{r}
read_csv("correlations_dat.csv") %>% 
  select(contains("weaver"), `Targeting Method`, `Measure`) %>% 
  set_names(c("aves_weaver_social", "Targeting Method", "Measure")) %>% 
  pivot_wider(names_from = `Measure`, values_from = aves_weaver_social) %>% 
  column_to_rownames("Targeting Method") %>% 
  heatmaply::heatmaply(show_dendrogram = c(FALSE, FALSE), main = "Aves Weaver Seeding Correlation Heatmap",
                       key.title = "Spearman")
```

